Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-23 ms.tex
correcting more of the analytics

Continuity of the entropy derivative at the stagnation radius where $v = 0$ requires that the temperature at this location be given by (eq.~[\ref{eq:first_law}])
\begin{align}
T|_{r_{s}}& = \frac{\gamma-1}{\gamma}\frac{\mu m_p
  \tilde{v}_{w}^{2}}{2k} \approx \frac{2}{5} \frac{7}{7-2\nu} \frac{\mu m_p
   v_{w}^{2}}{2k}\nonumber\\ 
 &\approx
 \begin{cases}
  4.5\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{core} \\
  5.3\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{cusp},
 \end{cases}
\label{eq:Tanalytic}
\end{align}
where we have assumed $\gamma=5/3$, $v_{500} \equiv v_{w}/(500$ km
s$^{-1}$) and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm
    s}}$ is the density power-law slope at $r = r_{\rm s}$.
Empirically, we find that
\begin{align}
\densSlope \simeq \frac{1}{6} \left(4 \Gamma+3\right).
\label{eq:densSlope}
\end{align}

Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
\begin{align}
  \rs=\frac{G \Mbh}{\densSlope
    v_w^{2}|_{\rs}}\left[\left(\frac{9-\Gamma}{2} -\densSlope\right)
    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{7}{2}-\densSlope\right].
\label{eq:stag_analytic}
\end{align}

If the SMBH dominates the gravitational potential at the stagnation
radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius
resides well inside the sphere of influence ($r_{\rm s} < r_{\rm
  soi}$; eq.~[\ref{eq:rsoi}]).  In this limit, equation
(\ref{eq:stag_analytic}) simplifies to
\begin{align}
  &\rs \underset{v_w \gtrsim \sigma}\approx \left(\frac{7}{2}-\densSlope\right)\frac{G \Mbh}{\densSlope v_w^2} \approx \begin{cases}
    9
 \, \pc \,\, \Mbheight v_{500}^{-2}\, \pyear& \text{core} \\
    4
 \, \pc \,\, \Mbheight v_{500}^{-2} \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:stag_simple}
\end{align}
where we have used equation~\eqref{eq:densSlope} to estimate
$\densSlope$: $\densSlope\approx 1$ and $\densSlope \approx 0.6$ for
core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.  This
expression is similar to that obtained by \citet{Volonteri+11} on more
heuristic grounds (their eq.~6).

>>>>

Continuity of the entropy derivative at the stagnation radius where $v = 0$ requires that the temperature at this location be given by (eq.~[\ref{eq:first_law}])
\begin{align}
T|_{r_{s}}& = \frac{\gamma-1}{\gamma}\frac{\mu m_p
  \tilde{v}_{w}^{2}}{2k} \approx \frac{\gamma-1}{\gamma}\frac{\mu
  m_p v_w^2}{2k} \frac{3+8\Gamma}{3+8\Gamma-6\nu} \nonumber\\ 
 &\approx
 \begin{cases}
  4.5\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{core} \\
  5.3\times 10^6\ \, v_{500}^2 \,\,{\rm K} & \text{cusp},
 \end{cases}
\label{eq:Tanalytic}
\end{align}
where we have assumed $\gamma=5/3$, $v_{500} \equiv v_{w}/(500$ km
s$^{-1}$), $v_w\gg\sigma_0$,  and $\densSlope \equiv -d{\rm ln}\rho/d{\rm ln\,r}|_{r_{\rm
    s}}$ is the density power-law slope at $r = r_{\rm s}$.
Empirically, we find that
\begin{align}
\densSlope \simeq \frac{1}{6} \left(4 \Gamma+3\right).
\label{eq:densSlope}
\end{align}

Hydrostatic equilibrium furthermore determines the value of the stagnation radius (Appendix \ref{app:rs}, eq.~\ref{eq:rs2main})
\begin{align}
 \rs=\frac{G \Mbh}{\densSlope (v_w^{2}+\sigma_0^2)}\left[2
    \frac{\Mstar|_{\rs}}{\Mbh} +\frac{13+ 8\Gamma}{4+2\Gamma}-\densSlope \frac{3}{2+\Gamma}\right].  
\label{eq:stag_analytic}
\end{align}

If the SMBH dominates the gravitational potential at the stagnation
radius, then $v_{w} \gtrsim \sigma$ and hence the stagnation radius
resides well inside the sphere of influence ($r_{\rm s} < r_{\rm
  soi}$; eq.~[\ref{eq:rsoi}]).  In this limit, equation
(\ref{eq:stag_analytic}) simplifies to
\begin{align}
  &\rs \underset{v_w \gtrsim \sigma}\approx
  \left(\frac{13+8\Gamma}{4+2\Gamma}-\densSlope
    \frac{3}{2+\Gamma}\right)\frac{G \Mbh}{\densSlope v_w^2}
  \approx \begin{cases} 9
    \, \pc \,\, \Mbheight v_{500}^{-2}\, \pyear& \text{core} \\
    4 \, \pc \,\, \Mbheight v_{500}^{-2} \, \pyear & \text{cusp},
  \end{cases}
  \label{eq:stag_simple}
\end{align}
where we have used equation~\eqref{eq:densSlope} to estimate
$\densSlope$: $\densSlope\approx 1$ and $\densSlope \approx 0.6$ for
core ($\Gamma = 0.1$) and cusp ($\Gamma = 0.8$) galaxies.  This
expression is similar to that obtained by \citet{Volonteri+11} on more
heuristic grounds (their eq.~6).
